---
title: "Project 3"
author: "Team members of Section 2"
date: "October 19, 2015"
output: html_document
---

### Project statement

This is a group project and we use Oscar Academy Awards data to determine whether Best Film Editing is the best predictor of Best Picture.

### Data set

The input data is from [link](https://github.com/aagoldberg/IS607/blob/master/tidedoscarwinners.csv). The 1's indicate winning the award, 0's indicate not winning.

### Techniques Used
1. Random Rorests
2. Training and Testing
3. Confusion Matrix

### Loading the data

```{r}
library(XML)
oscar_data <- readHTMLTable('tidedoscarwinners.csv.html')
oscar_data <- oscar_data[[1]]
head(oscar_data)
```

### Data cleaning

```{r}
oscar_data_ml <- oscar_data[,-c(1:4)]
head(oscar_data_ml)
dim(oscar_data_ml)
str(oscar_data_ml)
```

### Data Analysis

```{r}
library(lattice)
library(ggplot2)
library(caret)
set.seed(45)
inTrain <- createDataPartition(y=oscar_data_ml$Best_Picture, p=0.7,list=FALSE)
training <- oscar_data_ml[inTrain,]
testing <- oscar_data_ml[-inTrain,]
dim(training)
dim(testing)
library(randomForest)
model <- randomForest(Best_Picture ~., data=training)
model
importance(model)
library(caret)
predicted <- predict(model, testing)
table(predicted)
library(e1071)
confusionMatrix(predicted, testing$Best_Picture)
```

### Conclusion
With this dataset, Random forests provide a nice model to predict whether movie wins Best Picture or not. From the model, we can see Best_Directing is the strongest predictor, and Best_Editing is the next. 