---
title: "Untitled"
author: "KarenWeigandt"
date: "October 21, 2015"
output: html_document
---

Load necessary packages
```{r}
library(tidyr)
library(dplyr)
library(stringr)
```

Load Oscar data
```{r}
oscar_data <- read.csv("https://raw.githubusercontent.com/pm0kjp/IS607_Project3/master/data/Oscar_data.csv", stringsAsFactors = FALSE) ## latest tidied oscar data includes nominees
names(oscar_data)[names(oscar_data)=="Nominee"] <- "Movie" ## rename column
oscar_data$Movie[] <- trimws(oscar_data$Movie[]) ##get rid of white spaces at end that cause duplicates
oscar_data$Award[] <- trimws(oscar_data$Award[])
```

Work on list of Oscar films
```{r}
oscar_movie <- as.data.frame(oscar_data$Movie, stringsAsFactors = FALSE)
oscar_movie <- distinct(oscar_movie) # elimininate copies of the same movie
names(oscar_movie)[names(oscar_movie)=="oscar_data$Movie"] <- "film_title"  ## rename column to match EEP design
oscar_movie$oscar_nom_or_win <- 1
```

Work on list of Bafta films
```{r}
bafta_data <- read.csv("https://raw.githubusercontent.com/pm0kjp/IS607_Project3/master/data/tidybaftabestpicturewinners.csv", stringsAsFactors = FALSE)
bafta_data$pictures[] <- trimws(bafta_data$pictures[]) ##get rid of white spaces at end that cause duplicates

bafta_movie <- as.data.frame(bafta_data$pictures, stringsAsFactors = FALSE)
names(bafta_movie)[names(bafta_movie)=="bafta_data$pictures"] <- "film_title"  ## rename column to match EEP design
bafta_movie$bafta_best_pic_win <- 1
```

Join Oscar and bafta films
```{r}
oscar_and_bafta_movies <- dplyr::full_join(oscar_movie, bafta_movie, by = "film_title")
```


Work on list of SDFilm films
```{r}
sdfilm_data <- read.csv("https://raw.githubusercontent.com/pm0kjp/IS607_Project3/master/data/SDFilmAwards.csv", stringsAsFactors = FALSE)
sdfilm_data$Movie[] <- trimws(sdfilm_data$Movie[]) ##get rid of white spaces at end that cause duplicates


sdfilm_movie <- as.data.frame(sdfilm_data$Movie, stringsAsFactors = FALSE)
sdfilm_movie <- distinct(sdfilm_movie) # elimininate copies of the same movie
names(sdfilm_movie)[names(sdfilm_movie)=="sdfilm_data$Movie"] <- "film_title"  ## rename column to match EEP design
sdfilm_movie$sdfilm_award_win <- 1

```

Join SDfilm movies with previously joined Oscar and bafta films to create Film Table for database, then add film id to the data frame
```{r}
## join data frames
Film <- dplyr::full_join(oscar_and_bafta_movies, sdfilm_movie, by = "film_title")
## Put in alphabetical order
Film <- dplyr::arrange(Film, film_title)
## Change NAs to 0
Film$oscar_nom_or_win[is.na(Film$oscar_nom_or_win)]<-0
Film$bafta_best_pic_win[is.na(Film$bafta_best_pic_win)]<-0
Film$sdfilm_award_win[is.na(Film$sdfilm_award_win)]<-0

Film$film_id <- 1 ## Add column
Film$film_id <-seq.int(nrow(Film)) ## fill with category id integers

```
Film data frame complete

Work on Oscar_Award_Category dataframe
```{r}
## Separate out the awards
oscar_award <- as.data.frame(oscar_data$Award, stringsAsFactors = FALSE)
oscar_award <- distinct(oscar_award) # elimininate copies of the same award
names(oscar_award)[names(oscar_award)=="oscar_data$Award"] <- "award_category_name"  ## rename column to match EEP design
oscar_award$award_category_id <- 1 ## Add column
oscar_award$award_category_id <-seq.int(nrow(oscar_award)) ## fill with category id integers
oscar_award$oscar_nom_or_win <- 1
```
Oscar_Award_Category data frame complete

Work on Oscar_Award_Type data frame
```{r}
oscar_award_type <- as.data.frame(oscar_data$Winner, stringsAsFactors = FALSE)
names(oscar_award_type)[names(oscar_award_type)=="oscar_data$Winner"] <- "award_type_name"  ## rename column to match EEP design
oscar_award_type <- distinct(oscar_award_type) # elimininate copies of yes or no
oscar_award_type$award_type_name <- str_replace_all(oscar_award_type$award_type_name, "No", "Nominee")
oscar_award_type$award_type_name <- str_replace_all(oscar_award_type$award_type_name, "NO", "Nominee")
oscar_award_type$award_type_name <- str_replace_all(oscar_award_type$award_type_name, "Yes", "Winner")
oscar_award_type$award_type_name <- str_replace_all(oscar_award_type$award_type_name, "YES", "Winner")
oscar_award_type <- distinct(oscar_award_type) # elimininate copies of Winner or Nominee
oscar_award_type$award_type_id <- 0
oscar_award_type$award_type_id[2] <- 1
oscar_award_type$oscar_nom_or_win <- 1
```

