---
title: "Create CSVs for database upload - Film, Oscar_Award_Type, Oscar_Award_Category and Film_Oscar_Award"
author: "KarenWeigandt"
date: "October 21, 2015"
output: 
  html_document:
    toc: true
    toc_depth: 3
    theme: cerulean
---
### Introduction
Goal: To create .csv files for upload into the MySQL database for the following tables -  Film, Oscar_Award_Type, Oscar_Award_Category and Film_Oscar_Award.
#### IS 607 Section 2 Team is awesome.


### Load necessary packages
```{r}
library(tidyr)
library(dplyr)
library(stringr)
```

### Load Oscar data
```{r}
oscar_data <- read.csv("https://raw.githubusercontent.com/pm0kjp/IS607_Project3/master/data/tidyoscarnoms.csv", stringsAsFactors = FALSE)
names(oscar_data)[names(oscar_data)=="Nominee"] <- "Movie" ## rename column
```

### Work on list of Oscar films
```{r}
## Create data frame with film titles
oscar_movie <- as.data.frame(oscar_data$Movie, stringsAsFactors = FALSE)
names(oscar_movie)[names(oscar_movie)=="oscar_data$Movie"] <- "film_title"  ## rename column to match EEP design
```

### Work on list of Bafta films
```{r}
bafta_data <- read.csv("https://raw.githubusercontent.com/pm0kjp/IS607_Project3/master/data/tidybaftabestpicturewinners.csv", stringsAsFactors = FALSE)
bafta_data$pictures[] <- trimws(bafta_data$pictures[]) ##get rid of white spaces at end that cause duplicates

## Create data frame with film titles
bafta_movie <- as.data.frame(bafta_data$pictures, stringsAsFactors = FALSE)
names(bafta_movie)[names(bafta_movie)=="bafta_data$pictures"] <- "film_title"  ## rename column to match EEP design
```

### Join Oscar and bafta films
```{r}
oscar_and_bafta_movies <- dplyr::full_join(oscar_movie, bafta_movie, by = "film_title")
```


### Work on list of SDFilm films
```{r}
sdfilm_data <- read.csv("https://raw.githubusercontent.com/pm0kjp/IS607_Project3/master/data/SDFilmAwards.csv", stringsAsFactors = FALSE)
sdfilm_data$Movie[] <- trimws(sdfilm_data$Movie[]) ##get rid of white spaces at end that cause duplicates

## Create data frame with film titles
sdfilm_movie <- as.data.frame(sdfilm_data$Movie, stringsAsFactors = FALSE)
sdfilm_movie <- distinct(sdfilm_movie) # elimininate copies of the same movie
names(sdfilm_movie)[names(sdfilm_movie)=="sdfilm_data$Movie"] <- "film_title"  ## rename column to match EEP design
```

### Complete Film
Join SDfilm movies with previously joined Oscar and bafta films to create Film Table for database, then add film id to the data frame
```{r}
## join data frames
Film <- dplyr::full_join(oscar_and_bafta_movies, sdfilm_movie, by = "film_title")

## Attach column for film id
Film$film_id <- 1 ## Add column
Film$film_id <-seq.int(nrow(Film)) ## fill with category id integers

## Change the order of columns to match plan for database entry
Film <- Film[, c(2,1)]

head(Film)
```
Film data frame complete

create Film.csv file to be used for upload to MySQL database
```{r}
##  This creates the file in my working directory.  A copy of the file to is uploaded to Github to be accessible for database upload
write.csv(Film, file = "D:/IS607Workspace/Film.csv",row.names=FALSE)
```


### Work on Oscar_Award_Category dataframe
```{r}
## Separate out the awards
## Extract Award names
award_category_name <- colnames(oscar_data) ## name so column will match EEP design
award_category_name <-award_category_name[4:22]
Oscar_Award_Category <- as.data.frame(award_category_name, stringsAsFactors = FALSE)

Oscar_Award_Category$award_category_id <- 1 ## Add column
Oscar_Award_Category$award_category_id <-seq.int(nrow(Oscar_Award_Category)) ## fill with category id integers

head(Oscar_Award_Category)
```
Oscar_Award_Category data frame complete

create Oscar_Award_Category.csv file to be used for upload to MySQL database
```{r}
##  This creates the file on my working directory.  I will upload a copy of the file to the Github repository https://github.com/pm0kjp/IS607_Project3/tree/master/data to be accessible for database upload
write.csv(Oscar_Award_Category, file = "D:/IS607Workspace/Oscar_Award_Category.csv",row.names=FALSE)
```


### Work on Oscar_Award_Type data frame
```{r}
oscar_award_type_id <- c(1, 2)
oscar_award_type_name <- c("Winner", "Nominee" )
Oscar_Award_Type <- as.data.frame(cbind(oscar_award_type_id, oscar_award_type_name))

head(Oscar_Award_Type)
```
Oscar_Award_Type data frame complete

Oscar_Award_Type_Category.csv file to be used for upload to MySQL database
```{r}
##  This creates the file in my working directory.  A copy of the file to is uploaded to Github to be accessible for database upload
write.csv(Oscar_Award_Type, file = "D:/IS607Workspace/Oscar_Award_Type.csv",row.names=FALSE)
```


### Work on Film_Oscar_Award dataframe
```{r}
Film_Oscar_Award <- oscar_data

## Change Column names to use those planned for database film_oscar_award_id, film_id and convert category_name into category_id 
names(Film_Oscar_Award) <- c("film_oscar_award_id", "year", "film_id", 1:19)

## Convert film titles to film_id
Film_Oscar_Award$film_id <- c(1:nrow(Film_Oscar_Award))

## Gather into long format as expected by database
Film_Oscar_Award <- gather(Film_Oscar_Award, "oscar_award_category_id", "oscar_award_type_id", 4:22)

## Keep only those movies and awards for which they won or were nominated
Film_Oscar_Award <- filter(Film_Oscar_Award, oscar_award_type_id > 0)

## Convert variable type to integer as planned for database
Film_Oscar_Award$oscar_award_category_id <- as.integer(Film_Oscar_Award$oscar_award_category_id)

## Order by film id then by award category id
Film_Oscar_Award <- arrange(Film_Oscar_Award,film_id,oscar_award_category_id)

## Create unique ids for each entry in the table
Film_Oscar_Award$film_oscar_award_id <- c(1:nrow(Film_Oscar_Award))

## Change the order of columns to match plan for database entry
Film_Oscar_Award <- Film_Oscar_Award[, c(1,2,3,5,4)]

head(Film_Oscar_Award)
```


create Film_Oscar_Award.csv file to be used for upload to MySQL database
```{r}
##  This creates the file in my working directory.  A copy of the file to is uploaded to Github to be accessible for database upload
write.csv(Film_Oscar_Award, file = "D:/IS607Workspace/Film_Oscar_Award.csv",row.names=FALSE)
```

### Conclusion
This code uses the data provided by the team that did web scraping and data cleanup to reproducibly create 4 of the .csv files to be imported into the MySQL database. If you wish to reproduce it, please be sute to change the directory for saving the .csv files in the 4 appropriate sections.

